Whittaker Models for Real Groups

### 2024-06-07 whittaker.tex
Restores the lost discussion about Weyl chambers

Part~(c) follows from~\cite{rossmann_limit_orbits}.  Update May 1: it seems the right place is Lemma B, and to go from that to the statement is a matter of chasing definitions and using the asymptotic cone. \textcolor{blue}{Update May 29: by Lemma B in~\cite{rossmann_limit_orbits}, if $\mathfrak{h}^+$ is the large Weyl chamber containing the HC parameter of~$\pi$, then $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ is a single orbit---where $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ is defined in Rossmann's paper. What we have to check is that the closure of this $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains $\WF(\pi)$. Now, I think that  the equivalence between conditions  (L1) and (L2) on page 2 of~\cite{rossmann_limit_orbits} easily implies that the closure of $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains the asymptotic cone of the orbit of the HC parameter, so the claim seems to follow from the relationship between $\WF(\pi)$ and the asymptotic cone.}

@@

@@

>>>>

Part~(c) follows from~\cite{rossmann_limit_orbits}.  Update May 1: it seems the right place is Lemma B, and to go from that to the statement is a matter of chasing definitions and using the asymptotic cone. \textcolor{blue}{Update May 29: by Lemma B in~\cite{rossmann_limit_orbits}, if $\mathfrak{h}^+$ is the large Weyl chamber containing the HC parameter of~$\pi$, then $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ is a single orbit---where $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ is defined in Rossmann's paper. What we have to check is that the closure of this $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains $\WF(\pi)$. Now, I think that  the equivalence between conditions  (L1) and (L2) on page 2 of~\cite{rossmann_limit_orbits} easily implies that the closure of $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains the asymptotic cone of the orbit of the HC parameter, so the claim seems to follow from the relationship between $\WF(\pi)$ and the asymptotic cone (Lemma~\ref{lem:WF_and_AC}).}

@@

For this see \cite{HarrisHeOlafsson}; in our case the result is due to Rossmann and can be extracted from \cite{RossmannPicard}, Theorem B and C. \qed

@@

\subsection{Bonus}

This section uses the arguments above to deduce the ``folklore fact'' stated by  Jeff and Tasho with a reference to the present paper for the proof. \footnote{AA 2024-VI-7: I don't remember whether this was the most up-to-date version  of our understanding; I seem to remember that we wanted to know that $Q$ acts simply transitively on the large Weyl chambers, and I haven't thought yet about what the relationship this has with what is written below...}

We want to know that if $\pi_1=\pi(\lambda_1),\pi_2=\pi(\lambda_2)$ are large discrete series, then $\Wh(\pi_1)=\Wh(\pi_2)$ if and only $\lambda_1,\lambda_2$
are in the same Weyl chamber.

More precisely, $W$ and $W_K=\Norm_K(T)$ act on $T$, and $\pi(\lambda)=\pi(w\lambda)$ if and only if $\lambda\in W_K$.
So the correct statement is: $\Wh(\pi_1)=\Wh(\pi_2)$ if and only if the Weyl chambers of $\lambda_1,\lambda_2$ are conjugate by $W_K$.

One direction is easy using the above results: we have seen that if $\lambda_1,\lambda_2$
are in the same Weyl chamber then the wavefront set, therefore the Whittaker model, are the same.

What we need to show:
$\Wh(\pi(\lambda_1))=\Wh(\pi(\lambda_2)\Rightarrow \mathcal C(\lambda_1)$ is $W_K$-conjugate to  $\mathcal C(\lambda_2)$.

We may as well assume $\pi(\lambda_1),\pi(\lambda_2)$ are in the same $L$-packet, i.e. $\lambda_2=w\lambda_1$ for some $w\in W$.We know that $Q$ acts simply transitively on the large discrete series in the $L$-packet, and on principal nilpotent orbits.
Also: this action is given by the action of $W$, i.e. if $g\in Q$ then $\pi(\lambda)^g=\pi(g\lambda)=\pi(w\lambda)$ for some $w\in W$.
So
$$
\Wh(\pi_1)=\Wh(\pi_2)\Leftrightarrow \pi_1\simeq \pi_2\Leftrightarrow \lambda_1\sim_{W_K}\lambda_2\Leftrightarrow \mathcal C_1\sim_{W_K}\mathcal C_2
$$
